%============================= abs.tex================================
\begin{Abstract}
Speech recorded in a distant speech recording (DSR) scenario is corrupted by reverberation and noise resulting in poor quality recorded speech. This work proposes a novel non-negative matrix factorization (NMF) based single-channel enhancement method to handle reverberation and noise jointly. Such an approach is different from other NMF based approaches in the literature, which use a combination of convolutive NMF (CNMF) and NMF to model reverberation and noise. The proposed NMF model introduces better constraints on the room impulse response (RIR) that is not possible using other NMF based approaches.
We achieve the proposed NMF representation by introducing a low-rank factorization for the magnitude spectrogram of the RIR. We show that such a form accurately represents the RIR spectrogram.
Further, based on the RIR model, a supervised joint dereverberation and denoising method is proposed. The enhancement method is extended to work in unknown noise conditions. The performance of the proposed method has been validated on degraded utterances simulated from the TIMIT dataset and compared with other NMF based enhancement approaches. The objective measures indicate that the proposed enhancement method performs consistently better than other methods. The proposed method also gives a better estimate of the RIR magnitude spectrogram.
%
%
%
%
%
\end{Abstract}
%=======================================================================

